### 2024-02-15 documentation/thesis/thesis_document.tex
.

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field MRI research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analyzed throughout the study.

@@

Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
diagnostics, utilizing the principles of nuclear magnetic resonance
\gls{nmr} to generate cross-sectional black-and-white images of the
body. This indispensable method plays a crucial role in contemporary
medicine and research, contributing significantly to saving lives.
Despite its widespread use, traditional MRI systems often rely on large,
heavy, and expensive magnets to achieve the necessary homogeneity of the
magnetic field for accurate imaging. \cite{Nitz2016}

Various types of magnets find application in different \gls{mri}
systems. Permanent magnets generate a steady yet relatively weak
magnetic field, electro magnets are energized by electrical currents,
and superconducting electro magnets produce magnetic fields through
electric induction. Regardless of the type, the primary objective is to
create a homogeneous magnetic field within the \gls{mri}. The higher the
homogeneity, the more accurate the measurements. This uniform magnetic
field aligns the molecules within the body or object, setting the stage
for a second magnetic system to stimulate these molecules for
spin-measurements.

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary. In response to this, there
is a growing interest in developing low-field \gls{mri} systems that
utilize various magnet types, including permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While incapable of producing images due to lower magnetic
field strength, low-field systems facilitate the comparison of different
field behaviors and the identification of anomalies. O'Reilly and
Teeuwisse and de Gans \cite{OReilly2019-rn} have already
demonstrated low-cost and small-scale implementations with low-field
\gls{mri} in 2021.

Permanent magnets, usually arranged in a circular ``Halbach array''
around the \gls{mri}, are commonly employed in low-field systems.
However, their drawback is the inherent variability in strength,
complicating the achievement of a homogeneous field and requiring
precise strength information for correct magnet ordering and \gls{mri}
construction. Completed MRI systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment becomes formidable. An approach dictates that meticulous
adjustments to the magnets should be undertaken proactively, prior to
the finalization of the MRI system.

The focus of this thesis is on advancing low-frequency \gls{mri}
technology by addressing the sensor-usability of permanent magnets used
in these systems. The variability in the strength of permanent magnets
poses a significant obstacle to constructing an \gls{mri} with the
necessary precision for homogenous field generation.

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. The accompanying
open-source software is designed not only to facilitate measurements
with different sensors but also to enable the characterization of
different objects.

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1000\gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

This research initiative seeks to contribute to the improvement of
low-frequency \gls{mri} systems by enhancing the accuracy of permanent
magnet characterization. The outcomes of this thesis will provide
insights into the selection and evaluation of sensors for future
low-field \gls{mri} research, ultimately contributing to advancements in
medical imaging technologies.

@@

In the realm of modern medical imaging, high-field superconducting
magnets dominate most \gls{mri} machines, providing high blac-withe
image resolution. However, the substantial costs, space prerequisites,
and safety considerations associated with these systems pose
considerable challenges.

Magnetic resonance imaging \gls{mri} relies on the presence of a robust
magnetic field, and over time, there has been a continual push to
enhance the strength of these magnetic fields. This strength is
quantified in units of Tesla {[}T{]}, commonly referred to as the B0
field in medical contexts, while physicists use the term magnetic field
induction. The \gls{snr} is proprtional to the magnetic B0 field;
growing magnetic field leads automatically to higher \gls{snr}.

Notably, the focus on high-field systems predominated discussions until
around 1991 when the possibility of constructing \gls{mri} machines with
lower magnetic field strengths began to emerge. This marked a pivotal
shift in exploring the potential advantages and applications of
low-field \gls{mri} systems. \cite{Nitz2016}

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems measured between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri} is the improved
imaging of soft tissues, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}, cost reduction, a smaller device
footprint, alleviated safety concerns and leading to diminished image
resolution within clinically feasible scan durations.
\cite{Arnold2023-cn}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to 0.35 Tesla can be generated. However, this
achievement comes at the cost of an average system weight of 14 tons.
Despite their cost-effectiveness in production and maintenance,
permanent magnets exhibit drawbacks such as high temperature dependence
and a limited \gls{snr} due to the constrained field strength.
\cite{Nitz2016}

In particular, the advantages of the small design, the fast and simple
image acquisition and the low costs are advantages that will become
increasingly important in the future. However, the use of permanent
magnets and their structure is particularly important in such systems
and need to be analysed.

@@

The positioning of permanent magnets holds a pivotal role in
constructing an MRI and influencing the homogeneity of the B0 magnetic
field. Halbach ring magnets \cite{Halbach1980DesignOP} have become a
common design for low field \gls{mri} and \gls{nmr} systems
\cite{cmr.a.20165}.

@@

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \passthrough{\lstinline!12x12x12mm!} magnets are embedded to
generate homogeneous magnetic flux densities of around
\passthrough{\lstinline!20mT!}.

The homogeneity in this configuration depends, among other things, on
the following aspects:

@@

Halbach magnetic arrays present a compelling choice for mobile NMR due
to their ability to produce highly homogeneous and robust magnetic
fields per unit of magnetic mass, coupled with minimal stray fields. The
term ``Halbach Array'' (commonly known as ``magic rings'') denotes a
precise configuration of permanent magnets designed to amplify magnetic
flux on one side while concurrently mitigating or eliminating it on the
opposite side. \cite{inbook}

The Halbach magnetic array emerges as a crucial element for future
Magnet Characterization. Given that this thesis centers on assessing the
sensors' applicability, the Halbach magnetic array serves as a tool for
measurements, although its implementation and further discussion will
not be the primary focus.

@@

The shimming process is a crucial step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is crucial for high-resolution and
artifact-free images \cite{10.3389/fphy.2021.704566}.

Optimal homogeneity is attained through intricate designs facilitating
active shimming, a technique crucial for achieving high-resolution
spectroscopy. Beyond this, simpler combinations and adaptations of
Halbach rings offer versatility, making them suitable for variable field
magnets or magnets that can be effortlessly opened without applying
force. \cite{inbook}

@@

In this work, reference is made exclusively to the hardware shim
process. Since this project is to be used in the future to construct a
low-field \gls{mri} field magnet from permanent magnets.

@@

According to Wolfgang R. Nitz in 2016, just 13.4\% of actively used v
systems are low-field \gls{mri} (66.6\% 1.5T systems, 20\% 3.0 T system,
14.4\% low field with \textless0.5T). {[}Nitz2016{]} Nitz also
highlights that presently, the landscape of \gls{mri} technology is
dominated by a single manufacturer dealing with resistive magnets,
namely Stand-up \gls{mri} from FONAR Corp.~In contrast, the industry
giants such as Siemens, General Electric, Philips, Toshiba, among
others, predominantly rely on either permanent magnets or
superconducting magnets in their \gls{mri} systems. This notable
concentration underscores the distinctive position of Stand-up \gls{mri}
as a trailblazer in utilizing resistive magnets within the competitive
realm of magnetic resonance imaging. {[}Nitz2016{]}

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous 27cm diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019. This innovative setup was
subsequently employed in 2020 to acquire in vivo MR images, showcasing
the practical applications of their pioneering research
\cite{OReilly2021-ep}. 2023 veröffentlichten de Vos, Remis und Webb
eine zusammenfassung zur gestaltng eines oint-of-care halbach array
low-field \gls{mri} system \cite{De_Vos2023-pb}.

The objective of this \gls{mri} system is to prioritize
cost-effectiveness while efficiently capturing low-frequency images of
the head. The emphasis lies on swift and accurate imaging, achieved
through a streamlined approach that favors simplicity in the resultant
images. This \gls{mri} system is strategically designed with a primary
focus on cost-effectiveness, aiming to efficiently capture low-frequency
images of the head. The overarching goal is to achieve rapid and
accurate imaging through a simplified approach, prioritizing clarity and
ease in the resulting images.

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of
2400\gls{ppm} over a 20cm diameter using smaller magnets
(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
utilization of coil-based gradients for spatial encoding, significantly
enhancing the flexibility of image acquisition.

To further refine the magnet's homogeneity, optimization techniques are
employed by adjusting the radius of the Halbach cylinder along the
length of the magnet. The deliberate choice of smaller magnets, as
opposed to other Halbach designs, serves to compensate for inherent
manufacturing imperfections in each individual magnet. This strategic
decision not only mitigates structural demands on the magnet housing in
terms of strength and weight but also augments safety throughout the
construction process.

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets. Individual measuring points are
recorded. This data is then evaluated in separate software
\cite{Wickenbrock_2021}.

@@

Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
for breast) project, \emph{Fraunhofer MEVIS} in Bremen is actively
engaged in crafting a compact and mobile low-field \gls{mri} unit
tailored specifically for screening purposes. As described since 1991
low-field \gls{mri}s have evolved into a burgeoning realm of research,
showcasing substantial promise within the field of medical technology.
The endeavor by \emph{Fraunhofer MEVIS} exemplifies the ongoing
commitment to harnessing the potential of low-field \gls{mri} for
enhanced breast screening applications.

The focus of the ongoing efforts is to enhance the homogeneity of
magnets within low-field MRI systems below 1000\gls{ppm}, primarily
driven by the goal of establishing a compact low-field \gls{mri} for
breast cancer detection.

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field MRI system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
\gls{mri}, departing from the circular \gls{mri} configuration discussed
in the publication. This innovation is geared towards streamlining
breast examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition \emph{DeLoRI}
endeavors to achieve heightened accuracy, striving for precision levels
below 1000\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to
modify the ring diameter to influence field homogeneity, the unique goal
here is to characterize the magnets pre-installation, allowing for
proactive assessments of homogeneity characteristics. This nuanced
approach aims to provide insights into magnetic field uniformity before
the magnets are integrated, thereby streamlining the optimization
process. Furthermore,

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterization process.

To achieve this, a versatile hardware setup is in development, designed
to accommodate various sensors for the measurement of magnets or other
objects. Simultaneously, a software interface is being crafted to
universally read data from different sensors and interact seamlessly
with the diverse firmware associated with various Halbach sensors. A key
feature of this system is the ease of sensor interchangeability,
facilitating adaptability and versatility in the characterization
process.

The scope of the software library is to lay the foundation for the
systematic characterisation of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customization possible at each step of the process.
Complete documentation, tutorials and tests will enable users to use the
framework efficiently and adapt it to their specific requirements.

@@

Concerning the DeLoRI project, this study exclusively delves into the
realm of permanent magnets employed for creating a homogeneous B0 field
through Halbach rings. Other systems and spin generation for
measurements are deliberately excluded from consideration but will be
necessary in later stages of the DeLoRI project.

@@

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1000\gls{ppm}? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1000\gls{ppm}, with a specific
  focus on determining the sensors' viability for noise measurements.
\end{itemize}

It is crucial to emphasize that the intention is not to characterize the
magnets per se; rather, the emphasis lies in deriving meaningful
insights about the sensors deployed.

This work distinctly prioritizes the development of both hardware and
software tailored for sensor utilization and final testing. Physical
properties and considerations take a secondary role in comparison to the
overarching goal of refining the sensor-based methodologies.

@@

The following section defines some usecases that the future project
should be able to cover. These usecases define the setup of the hard-
and software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The usecases were defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is crucial for understanding the needs of the target group and
designing the end result accordingly.

@@

Finally, a comprehensive hardware and software framework must be
established, capable of measuring diverse objects using various sensors.
Additionally, conclusive remarks should be provided regarding the
suitability of the employed sensors for magnetic field measurements.

@@

A defined main objective of this project is the development of a
cost-effective magnetic field sensors interface that is also universally
expandable. The focus is on mapping different sensors and being
compatible with different magnet types and shapes.

This ensures a wide range of applications in different scenarios.
Another goal is reproducibility to ensure uniform results, which as a
result reduces the susceptibility to errors. Easy communication with
standard \gls{pc} hardware, which offers a variety of common interface
options, maximizes the user-friendliness.

@@

A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout.
The integration of integrated temperature sensors represents a
significant enhancement that will later enable precise temperature
compensation.

@@

The mechanical design of a sensor would be kept as simple as possible so
that it can be replicated as easily as possible. The focus was on
providing a stable foundation for the sensor \gls{ic} and an
exchangeable holder for different magnets.

@@

All parts were produced using the 3D printing additive manufacturing
processes. The sensor circuit board was glued underneath the magnet
holder. This is interchangeable, so different distances between sensor
and magnet can be realised.

@@

The focus here was on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation.

>>>>

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri}research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analyzed throughout the study.

@@

Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
diagnostics, utilizing the principles of nuclear magnetic resonance
\gls{nmr} to generate cross-sectional black-and-white images of the
body. This indispensable method plays a central role in contemporary
medicine and research, contributing significantly to saving lives.
Despite its widespread use, traditional \gls{mri} systems often rely on
large, heavy, and expensive magnets to achieve the necessary homogeneity
of the magnetic field for accurate imaging. \cite{Nitz2016}

Various types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electro magnets are energized by electrical currents, and
superconducting electro magnets produce magnetic fields through electric
induction. Regardless of the type, the primary objective is to create a
homogeneous magnetic field within the \gls{mri}. The higher the
homogeneity, the more accurate the measurements. This uniform magnetic
field aligns the molecules within the body or object, setting the stage
for a second magnetic system to stimulate these molecules for
spin-measurements.

The challenge with conventional homogeneity systems lies in their
substantial size, weight, and cost. Even when targeting smaller areas of
the body, large devices are often necessary.

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While tipically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviors and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\cite{OReilly2019-rn} have already demonstrated low-cost and
small-scale implementations with low-field \gls{mri} in 2021
calculationg images of a head sucessfully.

Permanent magnets, usually arranged in a circular ``Halbach array''
inside the \gls{mri}, are commonly used in low-field systems. However,
their drawback is the inherent variability in strength, complicating the
achievement of a homogeneous field and requiring precise strength
information for correct magnet ordering and \gls{mri} construction.

Completed \gls{mri} systems pose significant challenges for
retrospective adjustments, particularly when individual magnets impact
the overall homogeneity of the magnetic field. While deviations in
homogeneity can be measured post-assembly, the intricate task of
readjustment is taken into account. It is less costintensive and less
complicated to measure the magnets proactively, prior to the
finalization of the \gls{mri}system.

The focus of this thesis is to improve low-frequency \gls{mri}
technology by examining the usability of magnetic field sensors for
characterising permanent magnets used in these systems. The variability
in the strength of permanent magnets leads to significant difficulties
in constructing an \gls{mri} with the necessary precision for homogenous
field generation.

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other.

The accompanying open-source software for this thesis is designed not
only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

The sensor testing process involves three key test procedures for two
digital sensors. Firstly, the background noise for both sensors is
quantified by measuring with the sensors in a constant environment
without any magnets. Secondly, the linearity of the magnetic fields is
measured for all sensors to detect deviations from the estimated ideal
magnetic curve.

At last, the temperature drift is measured by repeating the background
noise test in different temperature environments. Sensor noise should be
less than \emph{50\(\mu\)T} to characterise precisely a magnetic field
in a Halbach-Array of an \gls{mri}with precision greater than
\emph{1000\gls{ppm}}.

This research initiative contributes to the improvement of low-frequency
\gls{mri} systems by enhancing the accuracy of permanent magnet
characterisation. The outcomes of this thesis provides insights into the
selection and evaluation of sensors for future low-field \gls{mri}
research, ultimately contributing to advancements in medical imaging
technologies.

@@

For modern medical imaging high-field superconducting magnets dominate
most \gls{mri} machines, providing high blac-withe image resolution.
However, the substantial costs, space requierments and safety
considerations cause considerable challenges.

\gls{mri} relies on the presence of a robust magnetic field, and over
time, there has been a continual push to enhance the strength of these
magnetic fields. This strength is quantified in units of Tesla {[}T{]},
commonly referred to as the \emph{B0} field in medical contexts, while
physicists use the term magnetic field induction. The \gls{snr} is
proprtional to the magnetic \emph{B0} field; growing magnetic field
leads automatically to higher \gls{snr}. The inital \emph{B0} field of
an \gls{mri} aims to be homogenouse, for image aquisition the second
step requires imhomoginity of the \emph{B0} field to stimulate spin in
the atoms of materials. For high resultion images, the initial \emph{B0}
field aims to be a homogenouse as possible.

Notably, the focus on high-field systems dominated discussions until
around 1991 when the possibility of constructing \gls{mri} machines with
lower magnetic field strengths came up. This marked a shift in exploring
the potential advantages and applications of low-field \gls{mri}
systems. \cite{Nitz2016}

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field \gls{mri}-systems measured between
\emph{0.1T} and \emph{0.3T} compared to the usual \emph{1.5T} to
\emph{3T} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri}s is the improved
imaging of soft material, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}, cost reduction, a smaller device
footprint, alleviated safety concerns and leading to diminished image
resolution within clinically feasible scan durations.
\cite{Arnold2023-cn}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
a limited \gls{snr} due to the constrained field strength.
\cite{Nitz2016}

In particular, the advantages of the small design, the fast and simple
image acquisition and the low costs are advantages that will become
increasingly important in the future. However, the use of permanent
magnets and their structure is particularly important in such systems
and needs to be analysed.

@@

The positioning of permanent magnets holds an important role in
constructing an \gls{mri} and is influencing the homogeneity of the
\emph{B0} magnetic field. Halbach ring magnets
\cite{Halbach1980DesignOP} have become a common design for low field
\gls{mri} and \gls{nmr} systems \cite{cmr.a.20165}.

@@

A halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

The homogeneity in this configuration depends, among other things, on
the following main aspects:

@@

Halbach magnetic arrays present a choice for mobile \gls{nmr} due to
their ability to produce highly homogeneous and robust magnetic fields
per unit of magnetic mass, coupled with minimal stray fields. The term
``Halbach Array'' (commonly known as ``magic rings'') denotes a precise
configuration of permanent magnets designed to amplify magnetic flux on
one side while concurrently mitigating or eliminating it on the opposite
side. \cite{inbook}

The Halbach magnetic array appears as a essential element for future
Magnet characterisation. Based on this fact this thesis centers on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

The shimming process is a essential step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is essential for high-resolution and
artifact-free images \cite{10.3389/fphy.2021.704566}.

Optimal homogeneity is attained through intricate designs facilitating
active shimming, a technique essential for achieving high-resolution
spectroscopy. Beyond this, simpler combinations and adaptations of
Halbach rings offer versatility, making them suitable for variable field
magnets or magnets that can be effortlessly opened without applying
force. \cite{inbook}

@@

In this thesis, reference is made exclusively to the hardware shimming
processes, since this project is to be used in the future to construct a
low-field \gls{mri} field magnet from permanent magnets.

@@

According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
\cite{Nitz2016}

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019.This innovative setup was subsequently
employed in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \cite{OReilly2021-ep}.
2023 veröffentlichten de Vos, Remis und Webb eine zusammenfassung zur
gestaltng eines oint-of-care halbach array low-field \gls{mri} system
\cite{De_Vos2023-pb}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
This innovative setup was subsequently employed in 2020 to acquire in
vivo MR images, showcasing the practical applications of their
pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
and Webb published a summary of the design of an oint-of-care halbach
array low-field \gls{mri} system \cite{De_Vos2023-pb}.

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
\emph{B0} field strength of 50.4mT, and an impressive homogeneity of
2400\gls{ppm} over a 20cm diameter using smaller magnets
(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
utilization of coil-based gradients for spatial encoding, significantly
enhancing the flexibility of image acquisition.

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
diameter using smaller magnets (\emph{12 x 12 x 12 mm\^{}3}). This
exceptional homogeneity enables the utilization of coil-based gradients
for spatial encoding, significantly enhancing the flexibility of image
acquisition.

To further refine the magnet's homogeneity, optimisation techniques are
employed by adjusting the radius of the Halbach ring along the length of
the magnet. The deliberate choice of smaller magnets, as opposed to
other Halbach designs, serves to compensate for inherent manufacturing
imperfections in each individual magnet. This strategic decision not
only mitigates structural demands on the magnet housing in terms of
strength and weight but also augments safety throughout the construction
process.

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets and individual measuring points are
recorded. This data is then evaluated in separate software
\cite{Wickenbrock_2021}.

@@

Within the framework of the \emph{DeLoRI} (Dedicated Low-field \gls{mri}
for breast) project, \emph{Fraunhofer MEVIS} in Bremen is actively
engaged in crafting a compact and mobile low-field \gls{mri} unit
customised specifically for screening purposes. As described before,
since 1991 low-field \gls{mri}s have evolved into a growing realm of
research, showcasing significant opportunities within the field of
medical technology. The efforts by \emph{Fraunhofer MEVIS} exemplifies
the ongoing commitment to utilizing the potential of low-field \gls{mri}
for enhanced breast screening applications.

The focus of the ongoing efforts is to improve the homogeneity of
magnets within low-field \gls{mri}systems below \emph{1000}\gls{ppm},
primarily driven by the goal of establishing a compact low-field
\gls{mri} for breast cancer detection.

Beyond the development and prototype construction of low-field \gls{mri}
scanners, the project encompasses electromagnetic simulation of
components within the low-field \gls{mri}system, coupled with machine
learning-driven control and data acquisition. The resultant software
will be instrumental in reconstruction, with a specific focus on
leveraging AI-based methodologies.

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, \emph{DeLoRI} aims to design an open
\gls{mri}, departing from the circular \gls{mri} configuration discussed
in the publication. This innovation is geared towards streamlining
breast examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation.

In addition \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below 1000\gls{ppm}. While O'Reilly,
Teeuwisse, and Webb were able to modify the ring diameter to influence
field homogeneity, the unique goal here is to characterize the magnets
pre-installation, allowing for proactive assessments of homogeneity
characteristics. This approach aims to provide insights into magnetic
field uniformity before the magnets are integrated, thereby streamlining
the optimisation process. Furthermore,

It is important to note that the primary objective of this thesis is not
merely to characterize the magnet itself; rather, the emphasis lies in
the selection and comparison of potential sensors for the
characterisation process.

To achieve this, a versatile hardware setup is in development, designed
to accommodate various sensors for the measurement of magnets or other
objects. Simultaneously, a software interface is being crafted to
universally read data from different sensors and interact seamlessly
with the diverse firmware associated with various Halbach sensors. A key
feature of this system is the ease of sensor interchangeability,
facilitating adaptability and versatility in the characterisation
process.

The scope of the software library is to lay the foundation for the
systematic characterisation of magnets based on permanent magnets. The
library will enable data acquisition, storage and analysis of magnetic
properties, with customisation possible at each step of the process.
Complete documentation, tutorials and tests will enable users to use the
framework efficiently and adapt it to their specific requirements.

@@

Concerning the \emph{DeLoRI} project, this study exclusively delves into
the realm of permanent magnets employed for creating a homogeneous
\emph{B0} field through Halbach rings. Other systems and spin generation
for measurements are deliberately excluded from consideration but will
be necessary in later stages of the \emph{DeLoRI} project.

Before naming the research focus, it is important to understand the
difference and connection between deviation and resulution of the
system. To measure a deviation of better than \emph{1000}\gls{ppm} in a
\emph{50mT} magnetic field, a resolution that is less than
\emph{1000}\gls{ppm} of \emph{50mT} is needed.

\[\frac{1000}{1000000} \times 50 \, mT = 0.05 \, mT \]

To convert this into microtesla (\(\mu\)T), a multiplication by
\emph{1000} is needed:

\[ 0.05 \, mT \times 1000 = 50 \, \mu T \]

This means that to measure a deviation of better than
\emph{1000}\gls{ppm} in a \(50mT\) magnetic field, a resolution of less
than \emph{50} \(\mu\)T is needed.

@@

\begin{itemize}
\item
  Sensor characterisation: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than \emph{1000}\gls{ppm}? The desired outcome
  is a measurement of less than \emph{50} \(\mu\)T at
  \emph{1000}\gls{ppm}, with a specific focus on determining the
  sensors' viability for noise measurements.
\end{itemize}

It is essential to emphasize that the intention is not to characterize
the magnets; the sensores which might be used for characterisation are
be analised and evaluated.

This work prioritises the development of both hardware and software
customised for sensor utilization and final testing. Physical properties
and considerations take a secondary role in comparison to the
overarching goal of refining the sensor-based methodologies.

@@

The following section defines possible usecases that the future project
need to cover. These usecases define the setup of the hard- and
software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The usecases were defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is essential for understanding the needs of the target group and
designing the end result accordingly.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which is capable of measuring diverse objects using various
sensors. Additionally, remarks need to be provided regarding the
suitability of the employed sensors for magnetic field measurements.

@@

A defined main objective of this project is the development of a
cost-effective magnetic field sensors interface that is universally
expandable as well. The focus is on mapping different sensors and being
compatible with different magnet types and shapes. This ensures a wide
range of applications in different scenarios.

Another goal is reproducibility to ensure uniform results, which as a
result reduces the susceptibility to errors. Easy communication with
standard \gls{pc} hardware, which offers a variety of common interface
options, maximizes the user-friendliness.

@@

A key aspect of this selection was the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout
since these kind of sensors are easy to integrate compared to
non-digital sensors, which require specific frameworks. The integration
of integrated temperature sensors represents a significant enhancement
that will later enable precise temperature compensation.

@@

The mechanical design of a sensor is kept as simple as possible so that
it can be replicated as easily as possible. The focus is on providing a
stable foundation for the sensor \gls{ic} and an exchangeable holder for
different magnets.

@@

All parts are produced using the 3D printing additive manufacturing
processes. The sensor circuit board was glued underneath the magnet
holder. This is interchangeable, so different distances between sensor
and magnet can be realised.

@@

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation.
